%!TEX root = main.tex

%__________________________________________________________________________________________________________________
% Publications
\section{\mysidestyle Publications}

Preprint\\
\begin{enumerate}[{label=[P\arabic*]}]
    \item \underline{Shucheng Kang} and Heng Yang.
    Simplicial regularizability of the pseudo-moment cone and Carathéodory-type atomic decomposition of moment matrices. \emph{SIAM Journal on Optimization}. \linkToPdf{https://arxiv.org/pdf/2605.06854} \linkToCode{https://github.com/ComputationalRobotics/momentcone-simregularity}

    \item \underline{Shucheng Kang} and Heng Yang.
    Local second-order limit dynamics of the alternating direction method of multipliers for semidefinite programming. Submitted to \emph{Mathematical Programming}. \linkToPdf{https://arxiv.org/pdf/2602.20103} \linkToCode{https://github.com/ComputationalRobotics/admmsdp-limitdyn}

    \item \underline{Shucheng Kang}, Haoyu Han, Antoine Groudiev, and Heng Yang. Factorization-free Orthogonal Projection onto the Positive Semidefinite Cone with Composite Polynomial Filtering. Submitted to \emph{SIAM Journal on Optimization} (minor revision). \linkToPdf{https://arxiv.org/pdf/2507.09165} \linkToCode{https://github.com/ComputationalRobotics/psd_projection/tree/main}
    
    \item \underline{Shucheng Kang}, Xin Jiang, and Heng Yang. Local linear convergence of the alternating direction method of multipliers for semidefinite programming under strict complementarity. Submitted to \emph{Mathematical Programming} (major revision). \linkToPdf{https://arxiv.org/pdf/2503.20142} \linkToCode{https://github.com/ComputationalRobotics/admmsdp-linearconv}
\end{enumerate}

Journal\\
\begin{enumerate}[{label=[J\arabic*]}]
    \item Lei Huang, \underline{Shucheng Kang}, Jie Wang, and Heng Yang. Sparse Polynomial Optimization with Unbounded Sets. \emph{SIAM Journal on Optimization}. 2025 \linkToPdf{https://arxiv.org/pdf/2401.15837.pdf} \linkToCode{https://github.com/wangjie212/TSSOS}
    
    \item Tianhao Wei, \underline{Shucheng Kang}, Weiye Zhao, and Changliu Liu. Persistently Feasible Robust Safe Control by Safety Index Synthesis and Convex Semi-infinite Programming. \emph{IEEE Control Systems Letters}. 2022 \linkToPdf{https://arxiv.org/pdf/2209.06896}
\end{enumerate}

Conference\\
\begin{enumerate}[{label=[C\arabic*]}]
    \item \underline{Shucheng Kang}, Guorui Liu, and Heng Yang. Global contact-rich planning with sparsity-rich semidefinite relaxations. \emph{Robotics: Science and Systems (RSS)}. 2025 \linkToPdf{https://arxiv.org/pdf/2406.05846} \linkToWeb{https://computationalrobotics.seas.harvard.edu/project-spot/} \linkToCode{https://github.com/ComputationalRobotics/SPOT}
    
    \item Yulin Li, Haoyu Han, \underline{Shucheng Kang}, Jun Ma, and Heng Yang. On the surprising robustness of sequential convex optimization for contact-implicit motion planning. \emph{Robotics: Science and Systems (RSS)}. 2025 \linkToPdf{https://arxiv.org/pdf/2502.01055} \linkToWeb{https://computationalrobotics.seas.harvard.edu/CRISP/} \linkToCode{https://github.com/ComputationalRobotics/CRISP}

    \item \underline{Shucheng Kang}, Xiaoyang Xu, Jay Sarva, Ling Liang, and Heng Yang. Fast and Certifiable Trajectory Optimization. \emph{International Workshop on the Algorithmic Foundations of Robotics (WAFR)}. 2024  \linkToPdf{https://arxiv.org/pdf/2406.05846} \linkToWeb{https://computationalrobotics.seas.harvard.edu/project-strom/} \linkToCode{https://github.com/ComputationalRobotics/cuADMM} \\
    \red{Best paper finalist, IEEE RAS TC on Model-based Optimization for Robotics, 2024} \\
    % \red{Spotlight, ``Safe Autonomy'' Workshop, Robotics: Science and Systems, 2024}\\
    % \red{``Frontiers of Optimization for Robotics" Workshop, Robotics: Science and Systems, 2024}\\
    % \red{Invited talk, ``International Conference on Continuous Optimization (ICCOPT)", 2025}
    
    \item \underline{Shucheng Kang}, Yuxiao Chen, Heng Yang, and Marco Pavone. Verification and Synthesis of Robust Control Barrier Functions: Multilevel Polynomial Optimization and Semidefinite Relaxation. \emph{IEEE Conference on Decision and Control (CDC)}. 2023 \linkToPdf{https://arxiv.org/pdf/2303.10081}
 
    \item Tianhao Wei, \underline{Shucheng Kang}, Ruixuan Liu, and Changliu Liu. Zero-shot Transferable and Persistently Feasible Safe Control for High Dimensional Systems by Consistent Abstraction. \emph{IEEE Conference on Decision and Control (CDC)}. 2023 \linkToPdf{https://arxiv.org/pdf/2303.10277}
    
    \item Xiang Zhu, \underline{Shucheng Kang}, and Jianyu Chen. A Contact-safe Reinforcement learning Framework for Contact-rich Robot Manipulation. \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}. 2022 \linkToPdf{https://arxiv.org/pdf/2207.13438}
\end{enumerate}

% Workshop\\
% \begin{enumerate}[{label=[W\arabic*]}]
%     \item Yang, Heng, and Pavone, Marco. Conformal Semantic Keypoint Detection with Statistical Guarantees. In \emph{NeurIPS Workshop on Robot Learning: Trustworthy Robotics}. 2022 \linkToPdf{https://drive.google.com/file/d/1GVhtBJB25qOZADqbIl926UmNWHeE0aD5/view?usp=sharing}
% \end{enumerate}