%!TEX root = main.tex

%__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Research Highlights}

    \textbf{Factorization-Free PSD Cone Projection via Composite Polynomial Filtering}

    \vquad Provides the first factorization-free PSD cone projection via a carefully designed \emph{Composite polynomial filter inspired by homomorphic encryption}. Shows up to \emph{$10\times$ speed-up} compared to state-of-the-art GPU-based eigenvalue solver while achieving moderate accuracy. Package written in \emph{C++} and \emph{CUDA}.

    \vquad Submitted \textit{SIAM Journal on Optimization'25}. 
    \href{https://arxiv.org/pdf/2507.09165}{[Paper]}
    \href{https://github.com/ComputationalRobotics/psd_projection/tree/main}{[Code]}

    \textbf{Local Linear Convergence Rate of ADMM for SDP}

    \vquad Establishes theoretical foundation for Alternating Direction Method of Multiplier (ADMM)'s \emph{local linear convergence rate} in semidefinite programming (SDP) under strict complementarity. Offers \emph{the first numerical observation} for ADMM's sharp local linear convergence rate over extensive datasets.
        
    \vquad Submitted \textit{Mathematical Programming'25}. 
    \href{https://arxiv.org/pdf/2503.20142}{[Paper]}
    \href{https://github.com/ComputationalRobotics/admmsdp-linearconv}{[Code]}

    \textbf{Global Contact-Rich Planning with Sparsity-Rich Semidefinite Relaxation}

    \vquad Shows that contact-rich motion planning is also \emph{sparsity-rich} when viewed as polynomial optimization (POP). Introduces the \emph{Sparse Polynomial Optimization Toolbox (SPOT)} — implemented in C++ with interfaces to both Python and Matlab — that automates sparsity exploitation for robotics and beyond.

    \vquad Accepted by \textit{Robotics: Science and Systems (RSS)'25}. 
    \href{https://arxiv.org/pdf/2406.05846}{[Paper]} 
    \href{https://computationalrobotics.seas.harvard.edu/project-spot/}{[Website]}
    \href{https://github.com/ComputationalRobotics/SPOT}{[Code]}
    

    \textbf{Fast and Certifiable Trajectory Optimization} 

    \vquad A powerful framework to compute \emph{certifiably optimal solutions} for \emph{nonconvex trajectory optimization} problems defined by polynomial objectives and constraints. The \emph{first GPU-based} large-scale SDP solver implemented in GPU. Achieves up to \emph{$10\times$ speed-up} compared to existing solvers and runs in real time when combined with data-driven warm-starts. Package written in \emph{C++} and \emph{CUDA}.
        
    \vquad Accepted by \textit{The 16th International Workshop on the Algorithmic Foundations of Robotics (WAFR)'24}. \href{https://arxiv.org/pdf/2502.02829}{[Paper]} 
    \href{https://computationalrobotics.seas.harvard.edu/project-strom/}{[Website]}
    \href{https://github.com/ComputationalRobotics/cuADMM}{[Code]}

    \textbf{Sparse Polynomial Optimization with Unbounded Sets}

    \vquad Extends sparse Moment-SOS Hierarchy to \emph{unbounded sets with homogenization techniques}. New asymptotic convergence guarantees are established.
        
    \vquad Accepted by \textit{SIAM Journal on Optimization'25}. 
    \href{https://arxiv.org/pdf/2401.15837}{[Paper]}
    \href{https://github.com/wangjie212/TSSOS}{[Code]}

    % \textbf{Verification and Synthesis of Robust Control Barrier Functions}

    % \vquad Provides a \textit{multi-level polynomial optimization framework} for robust CBF verification and synthesis. Asymptotic global convergence to optimality is guaranteed.

    % \vquad Accepted by \textit{CDC'23}. \href{https://arxiv.org/pdf/2303.10081}{[Paper]}